Quality Metrics for SKOS Vocabularies

### 2012-03-11 background.tex
structured contents; added TODOs

\section{Background and Definitions}

% About Data Quality and SKOS

SKOS is a language for defining vocabularies in the Web of Data and therefore based on the Open World Assumption. Established quality notions from closed-world systems, such as constraints, referential integrity or schema validation, don’t hold anymore, because the available information may be incomplete and facts that are not explicitly stated cannot be determined as true or false. While trust and provenance models for Web data are being developed \cite{Omitola2011,Hartig2009}, content-based and hand-crafted heuristics are currently used to evaluate quality in Linked Data sets \cite{Heath2011}.

% What kind of quality criteria are defined in SKOS

\todo{CM}{write a short paragraph about the quality criteria in the SKOS specification.}

% This definition is not a quality criterions, henec it is in the background section (we need to discuss that)

\begin{definition} \textbf{The SKOS Baseline Model} is defined as follows:
Let R be the set of all resources, as defined in [Web Architecture Document] and \[V = (C, A, LL, LR, SR, AR)\] be one specific SKOS vocabulary, with

\begin{itemize}
	\item \(C \subseteq R\) being the set of \textbf{conceptual resources} of type \texttt{skos:Concept}.
	\item \(A \subseteq R\) being the set of aggregation and grouping resources in SKOS, hence \texttt{skos:ConceptSchema} and \texttt{skos:Collection}.
	\item LL being the set \textbf{lexical labels}, which are instances of RDF plain literals.
	\item \(LR \subseteq C \times LL\) being the set of \textbf{lexical relations} associating conceptual resources with lexical labels, hence instances of \texttt{skos:prefLabel}, \texttt{skos:altLabel}, or \texttt{skos:hiddenLabel}.
\item \(SR \subseteq C \times C\) being the set of \textbf{semantic relations} associating conceptual resources with concepts, hence instances of \texttt{skos:semanticRelation} and subproperties thereof.
\item \(AR \subseteq C \times A\) being the set of \textbf{aggregation (and grouping) relations} associating conceptual resources with instances of aggregation and grouping resources.
\end{itemize}
\end{definition}

>>>>

\section{Background and Methodology}

% About Controlled Vocabulary Quality

\todo{CM}{After the introduction it is very common to introduce the problem in more detail. We should write a page about quality in controlled vocabularies and explain the sources for our quality metics. Maybe you can pull parts from the related work section.}

% Methodology

\todo{CM}{How did we identify the criteria we present in the following section?}

%SKOS is a language for defining vocabularies in the Web of Data and therefore based on the Open World Assumption. Established quality notions from closed-world systems, such as referential integrity or schema validation, don’t hold anymore, because the available information may be incomplete and facts that are not explicitly stated cannot be determined as true or false. While trust and provenance models for Web data are being developed \cite{Omitola2011,Hartig2009}, content-based and hand-crafted heuristics are currently used to evaluate quality in Linked Data sets \cite{Heath2011}.

### 2012-03-11 introduction.tex
structured contents; added TODOs

The SKOS specification doesn't make any explicit statements about vocabulary quality. It defines a set of \textbf{integrity conditions} that state ``whether or not given data are consistent with respect to the SKOS data model'' [\todo{SKOS reference}]. Existing quality checking tools, such as the PoolParty Thesaurus Consistency Checker\footnote{\url{http://demo.semantic-web.at:8080/SkosServices/check}} or SKOSify\footnote{\url{http://code.google.com/p/skosify/}} can be used to verify that a given vocabulary fulfills these conditions. However, these conditions fail to capture \textbf{quality criteria} such as those mentioned in the examples before; criteria that go beyond the SKOS data model. Such criteria might be part of design rules and guidelines, but rely on \textbf{human assessment}, which is highly subjective and doesn’t scale for larger, possibly linked Web vocabularies.

@@

The goal of our work is to identify possible quality criteria for controlled vocabularies and to provide a set of quantitative quality indicators for SKOS vocabularies. We believe that this can help domain experts in judging the quality of existing or newly created vocabularies and provide important feedback to the overall vocabulary design process. The main contributions of this work can be summarized as follows:

@@

	\item We identified \textbf{quality criteria} for controlled vocabularies by examing existing literature, tools, and public mailing list discussions.

	\item We \textbf{formalized} them into computable \textbf{quality metrics} and implemented them in the \textbf{qSKOS quality assessment tool}.

>>>>

The SKOS specification doesn't make any explicit statements about vocabulary quality. It defines a set of \textbf{integrity conditions} that state ``whether or not given data are consistent with respect to the SKOS data model'' [\todo{SKOS reference}]. Existing quality checking tools, such as the PoolParty Thesaurus Consistency Checker\footnote{\url{http://demo.semantic-web.at:8080/SkosServices/check}} or SKOSify\footnote{\url{http://code.google.com/p/skosify/}} can be used to verify that a given vocabulary fulfills these conditions. However, these conditions fail to capture \textbf{quality criteria} such as those mentioned in the examples before; criteria that go beyond the SKOS data model. Such criteria might be part of design rules and guidelines, but rely on \textbf{human judgement}, which is subjective and does not scale for larger, possibly linked Web vocabularies.

@@

The goal of our work is to provide a set of quantitative quality indicators for SKOS vocabularies. We believe that this can help domain experts in judging the quality of existing or newly created vocabularies and provide important feedback to the overall vocabulary design process. The main contributions of this work can be summarized as follows:

@@

	\item We identified \textbf{quality criteria} for controlled vocabularies by examining existing literature, tools, and public mailing list discussions. Then we \textbf{formalized} them into computable \textbf{quality metrics} so that they can be implemented consistently by different tools.

	\item We implemented these metrics in the \textbf{qSKOS quality assessment tool}.
